\documentclass[margin,line]{res}
\usepackage{multicol, enumitem, url, float, hyperref}

\usepackage[backend=biber,
            sorting=none,
            defernumbers=true,
            firstinits=true,
            maxbibnames=99,
            hyperref=true]{biblatex} % load the package
\DeclareNameAlias{author}{last-first}
\renewbibmacro{in:}{} % get rid of "In:"
\addbibresource{bib/papers.bib}
\addbibresource{bib/posters.bib}
\addbibresource{bib/packages.bib}
\addbibresource{bib/talks.bib} % add a bib-reference file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% bib links
% https://tex.stackexchange.com/questions/48400/biblatex-make-title-hyperlink-to-dois-url-or-isbn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newbibmacro{string+doiurlisbn}[1]{%
  \iffieldundef{doi}{%
    \iffieldundef{url}{%
      \iffieldundef{isbn}{%
        \iffieldundef{issn}{%
          #1%
        }{%
          \href{http://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
        }%
      }{%
        \href{http://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
      }%
    }{%
      \href{\thefield{url}}{#1}%
    }%
  }{%
    \href{http://dx.doi.org/\thefield{doi}}{#1}%
  }%
}

\DeclareFieldFormat{title}{\usebibmacro{string+doiurlisbn}{\mkbibemph{#1}}}
\DeclareFieldFormat[article,incollection]{title}%
    {\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}
\DeclareFieldFormat{url}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\pagestyle{plain} % page numbers
 

\begin{document}
\nocite{*}
\name{Andee Kaplan \vspace*{.1in}}

\begin{resume}

\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Department of Statistics  & {\it E-mail:} andee.kaplan@colostate.edu\\
Colorado State University &  {\it WWW:} \url{https://andeekaplan.com} \\
Fort Collins, CO 80523-1877 & ORCID: 0000-0002-2940-889X\\
\end{tabular}

\section{\sc Education}
{\bf Ph.D. in Statistics}, Iowa State University, Ames, IA \hfill 2017 \\
{\bf M.S. in Statistics}, Iowa State University, Ames, IA \hfill 2014 \\
{\bf M.A. in Mathematics}, The University of Texas, Austin, TX \hfill 2010 \\
{\bf B.S. in Mathematics}, The University of Texas, Austin, TX \hfill 2006 


\section{\sc Professional Appointments}
{\bf Assistant Professor} \hfill August 2019 -- Present \\
Department of Statistics, Colorado State University,  Fort Collins, CO\\
{\bf Postdoctoral Associate}  \hfill August 2017 -- July 2019 \\
Department of Statistical Science, Duke University, Durham, NC 


% \section{\sc Selected Honors and Awards}
% {\em Selected for ``The Best of JCGS -- Invited Papers" Session at JSM } \hfill 2019\\
% ``Designing Modular Software: A Case Study in Introductory Statistics" with E. Hare selected for inclusion in the session.

\section{\sc Teaching Experience}
*Denotes new courses developed.\\

\vspace{-.4cm}

\begin{table}[H]
\begin{tabular}{l l}
\multicolumn{2}{l}{{\bf Colorado State University}} \hfill Semester (Enrollment; Honors Options) \\
STAT 630 & Advanced Statistical Data Analysis (3 credit hours [cr])  \hfill  F23 (10) \\
STAA 577 & Statistical Learning and Data Mining (2 cr)   \hfill  S23 (14), F23 (7)\\
DSCI 445* & Statistical Machine Learning (3 cr)  \hspace{.8cm} \hfill F20 (8; 1), F21 (32), F22 (28; 1) , F23 (27) \\
STAT 400 & Statistical Computing (3 cr)  \hfill  F19 (15; 1), F20 (19), F21 (24), F22 (16) \\
STAT 730 & Advanced Theory of Statistics I (4 cr)  \hfill  S20 (6) \\
\end{tabular}
\end{table}

\section{\sc Open Course Materials}
STAT400 Statistical Computing (\url{https://stat400-csu.github.io}) \\
DSCI445 Statistical Machine Learning (\url{https://dsci445-csu.github.io}) \\
STAT630 Advanced Statistical Data Analysis(\url{https://stat630-csu.github.io})


\section{\sc Advising}

{\bf Doctoral Student Advising} \hfill \\
Hannah Butler (Statistics, 2022 -- ) \\
Lane Drew (Statistics, 2021 -- ) \\
Ian Taylor (Statistics, Co-advisor: Bailey Fosdick, 2020 -- ) \\
\vspace{-.5cm}

{\bf Doctoral Committee Member} \hfill \\
Wilson Wright, (Statistics, 2023 -- )\\
Justin Van Ee (Statistics, PhD 2023) \\
Connor Gibbs (Statistics, PhD 2023)  \\
Alex Fout (Statistics, PhD 2022) \\
Xinyi (Lucy) Lu, (Statistics, PhD 2021) \\

\vspace{-.5cm}
{\bf Undergraduate Honors Thesis Committee Member} \hfill \\
Olivia Beck (Statistics, Fall 2019) \\

\vspace{-.5cm}
{\bf Directed Undergraduate Research} \hfill \\
Caleb Chou (Data Science, Summer 2023) \\
Ryan Volkert (Data Science, Spring 2021) \\

\section{\sc Selected Service and Leadership}

{\bf Colorado State University} \\
Data Science Research Institute Steering Committee \hfill {2020 -- Present} \\

\vspace{-.3cm}
{\bf College of Natural Science, Colorado State University} \\
Data Science Committee to Explore Graduate Programs \hfill {2022} \\

\vspace{-.3cm}
{\bf Department of Statistics, Colorado State University} \\
Graduate Admissions Committee \hfill {2020-2021, 2022 -- Present} \\
Diversity, Equity and Inclusion Committee \hfill {2023 -- Present} \\
Undergraduate Committee \hfill {2022 -- 2023} \\
%Search Committee \hfill {Fall 2021 - Spring 2022} \\
%Search Committee \hfill {Fall 2020 - Spring 2021} \\
Co-organizer Statistical Learning and Data Science Journal Club \hfill {2020} \\
%Seminar Co-organizer \hfill {Fall 2019 - Spring 2020} \\

\section{\sc Publications}


{\bf Selected Peer-reviewed Publications} (*Denotes mentored student) \\
\begin{enumerate}
\item Lu, X.*, Hooten, M. B., {\bf Kaplan, A.}, Womble, J. N., and Bower, M. R. (2022). Improving wildlife population inference using aerial imagery and entity resolution. {\em Journal of Agricultural, Biological and Environmental Statistics}, 27(2), 364-381.
\item Marchant, N. G.*, {\bf Kaplan, A.}, Elazar, D. N., Rubinstein, B. I., and Steorts, R. C. (2021). d-blink: Distributed end-to-end Bayesian entity resolution. {\em Journal of Computational and Graphical Statistics}, 30(2), 406-421.
\item Hare, E. and {\bf Kaplan, A.}, 2017. Designing modular software: a case study in introductory statistics. {\em Journal of Computational and Graphical Statistics}, 26(3), pp.493-500.
\end{enumerate}


{\bf Selected Manuscripts Submitted and Under Revision} (*Denotes mentored student) \\
\begin{enumerate}
\item Taylor, I.*, {\bf Kaplan, A.}, and Betancourt, B. Fast Bayesian Record Linkage for Streaming Data Contexts. Revision submitted to {\em Journal of Computational and Graphical Statistics}.
\item Biswas, E.*, {\bf Kaplan, A.}, and Nordman, D. A formal goodness-of-fit test for spatial binary Markov random field models. Submitted to {\em Biometrics}.
\item Taylor I.*, {\bf Kaplan, A.}, and Betancourt, B. Generative Filtering for Recursive Bayesian Inference with Streaming Data. Submitted to {\em Journal of the American Statistical Association}.
\end{enumerate}

{\bf Selected Manuscripts in Preparation} (*Denotes mentored student or postdoc) \\
\begin{enumerate}
\item Lu, X.*, \mkbibbold{Kaplan, A.}, Kanno, Y.,Valentine, G., Rash, J., and Hooten, M. B. Stochastic Spatial Stream Networks.
\item Drew, L.*, {\bf Kaplan, A.}, and Breckheimer, I. An Entity Resolution Approach to Tree Demography with Lidar Data.
\item Butler, H.*, {\bf Kaplan, A.} Leveraging Bayesian Entity Resolution to Illuminate the Lives of Freedom Seekers in 19th Century America.
\item Chou, C.*, {\bf Kaplan, A.} The Fast and the Furious: Tracking the Effect of the Tomoa Skip on Speed Climbing.
\end{enumerate}









\end{resume}
\end{document}
